\begin{thebibliography}{99999}
\phantomsection
\singlespace\normalsize

% \bibitem{Ak} Akins R.E. Performance evaluation of wind-energy conversion systems using the method of bins - current status. Internal.Report SAND-77-1375. Sandia Laboratory, USA, 1978. 

% \bibitem{And}Anderson J.D., Fundamentals of aerodynamics, 2nd Edition. McGraw-Hill, Singapore.

% \bibitem{booch} Booch G. et. al\textit{., }Object-Oriented Analysis and Design with
% Applications, Addison-Wesley 2007.

% \bibitem{Bostan}
% Bostan I., Dulgheru V., Sobor I., Bostan V., Sochirean A., Sisteme de
% conversie a energiilor regenerabile, Technica-Info 2007.

% \bibitem{Xfoil}Drela M. Xfoil : An Analysis and Design System for Low Reynolds Number Airfoils. Low Reynolds Number Aerodynamics, Springer-Verlag, Lec. Notes in Eng. 54, 1989.

% \bibitem{gamma} Gamma E., Helm R., Johnson R., Vlissides J.\textit{, }Design Patterns -
% Elements of Reusable Object-Oriented Software, Addison-Wesley 1994.

% \bibitem{Larman1} Larman C., Agile and Iterative Development: A Manager's Guide, Adisson
% Wessley 2003.

% \bibitem{Larman2} Larman C., Applying UML and Patterns: An Introduction to Object-Oriented
% Analysis and Design and the Unified Process, Addison Wessley 2002.

% \bibitem{PITAC} President’s Information Technology Advisory Committee, Computational Science: Ensuring America’s Competitiveness, Report to President, \url{http://www.nitrd.gov/pitac/reports/20050609_computational/computational.pdf}, June 2005. 

% \bibitem{CwithUML} \url{http://www.drdobbs.com/184401948}

% \bibitem{Pic1}Super-sized 6.15MW Wind Turbine Up and Running, 2050 Magazine, \url{http://www.2050publications.com/super-sized-6-15mw-wind-turbine-up-and-running/}

% \bibitem{Pic2}Largest Wind Farm in Europe Alive, \url{http://www.renewindians.com/2012/12/Largest-Wind-Farm-in-Europe.html}

% \bibitem{Pic3}GE Power \& Water, Renewable energy, \url{http://www.ge-renewable-energy.com/uploads/tx_spdownloads/Fantanele_Romania_2.xWEA_03.JPG}

	\bibitem{naoDocumentation}
		Aldebaran Robotics.
		\emph{NAO Software 1.14.4 documentation}.
		 \url{www.community.aldebaran-robotics.com/doc/1-14/index.html}

		 	\bibitem{webots}
		Cyberbotics.
		\emph{Webots overview}.
		\url{www.cyberbotics.com/overview}

		 	\bibitem{objectGrasping}
		Egbert van der Wal.
		\emph{Object Grasping with the NAO: master's thesis}.
		Department of AI, 
		University of Groningen,
		The Netherlands.
		\url{www.ai.rug.nl/~mwiering/thesis\_Egbert\_van\_der\_Wal.pdf}

		 \bibitem{naoWiki}
		Endgadget.
		\emph{Nao robot replaces AIBO in RoboCup Standard Platform League}
		\url{www.engadget.com/2007/08/16/nao-robot-replaces-aibo-in-robocup-standard-platform-league/}

			\bibitem{shadowRemoval}
		Fredembach C., Finlayson G.
		\emph{Simple Shadow Removal}.
		\url{www.ivrgwww.epfl.ch/alumni/fredemba/papers/FFICPR06.pdf}




	\bibitem{graspingKnownObjects}
		Gupta A., Frese U., Dawood M.
		\emph{Grasping Known Objects with Aldebaran Nao}.
		\url{www.cse.iitk.ac.in/users/cs365/2012/submissions/ashug/cs365/projects/report.pdf}

 	\bibitem{objectLearning}
		Heinrich S., et. al.
		\emph{Object Learning with Natural Language in a Distributed Intelligent System --
		A Case Study of Human-Robot Interaction}.
		Department of Informatics,
		University of Hamburg.
		\url{www.informatik.uni-hamburg.de/WTM/ps/Heinrich\_CSIP2012\_CR.pdf}

 	\bibitem{visualGrasping}
		Holl T., Pinz A.
		\emph{Vision-based grasping of objects from a table using the humanoid robot Nao}.
		Inst. of Electrical Measurement and Measurement Signal Processing Graz Univ. of Technology, Austria.
		\url{www.emt.tugraz.at/system/files/ARW\_2011.pdf}

		\bibitem{naoPhoto1}
		Image with NAO.
		\emph{Aldebaran Robotics NAO Next Gen Fully Programmable Humanoid Robot Review}
		\url{www.goo-android.blogspot.com/2011/12/aldebaran-robotics-nao-next-gen-fully.html}

	\bibitem{grabAMug}
		Muller J., Frese U., Rofer T.
		\emph{Grab a Mug – Object Detection and Grasp Motion Planning with the Nao Robot}.
		\url{www.informatik.uni-bremen.de/agebv2/downloads/published/muellerhumanoids12.pdf}

			\bibitem{ml}
		Ng A. 
		\emph{Machine Learning course}.
		\url{www.coursera.org/course/ml}

			\bibitem{slides}
		Ng A. 
		\emph{Machine Learning course}.
		Slides from lecture 13-14.
		\url{www.coursera.org/course/ml}

	\bibitem{opencv}
		OpenCV Dev Team.
		\emph{OpenCV 2.4.9.0 documentation}.
		\url{www.docs.opencv.org/modules/refman.html}

\bibitem{robotics}
		Oxford Dictionaries.
		\emph{Robotics}
		\url{www.oxforddictionaries.com/definition/english/robotics}

			\bibitem{prati}
		Prati, A., et. al.
		\emph{Detecting Moving Shadows: Formulation, Algorithms and Evaluation}.
		\url{www.cvrr.ucsd.edu/aton/publications/pdfpapers/TRshadow.pdf}

 	\bibitem{categorization}
		Ramanathan V., Pinz A.
		\emph{Active robot categorization on a humanoid robot}.
		\url{www.cs.stanford.edu/~vigneshr/papers/visapp11.pdf}

\bibitem{tooBigToIgnore}
		Simon, P.
		\emph{Too Big to Ignore: The Business Case for Big Data}.
		1st ed.
		Wiley,
		March 18, 2013.
		ISBN 978-1118638170.
	 	p. 89.

	 		\bibitem{suzuki}
		Suzuki S., Abe K.
		\emph{Topological Structural Analysis of Digitized Binary Images by Border Following}.
		pp 32-46, 1985.
		\url{wenku.baidu.com/view/6cb52ede360cba1aa811dad5.html}








	\bibitem{zivkovic}
		Zivkovic Z. 
		\emph{Improved adaptive Gausian mixture model for background subtraction}.
		International Conference Pattern Recognition.
		UK, August, 2004.
		\url{www.zoranz.net/Publications/zivkovic2004ICPR.pdf}

	\bibitem{heijden}
		Zivkovic, Z., Heijden, F. van der,
		\emph{Efficient Adaptive Density Estimation per Image Pixel for the Task of Background Subtraction}.
		Pattern Recognition Letters,
		vol. 27, no. 7, pp 773-780, 2006.






	% \bibitem{ramer}
	% 	Wikimedia Foundation.
	% 	Ramer-Douglas-Peucker Algorithm. In \emph{Wikipedia: The Free Encyclopedia}
	% 	[online].
	% 	[cited 2014-04-28].
	% 	English version.
	% 	Available from:
	% 	\url{en.wikipedia.org/wiki/Robotics}









\end{thebibliography}
